timesliced_random_cell_selection

### 2018-11-09 src/raster_sjl.Rmd
loop works! Just trying something else out

```{r}
netcdf_list <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf){  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working one
  brkyr <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 1)) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 2)) # extracting the second part of the netcdf filename (which is the month)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:nrow(obssp)) {  
      print (j)
      de <- obssp$depth[[j]]  # a variable for the observation depth layer
      yr <- (obssp$year[j])  # a variable for the observation year
      mth <- (obssp$month[j])  # a variable for the observation month
      #I think i need an if statement here... if brkyr == yr & brkmth == mth do the data extraction below
        #for (k in 1:nrow(obssp)){
          if (brkyr == yr & brkmth == mth){
            obssp$salinity_surface[j] <- extract(x=temp_brick[[1]], y = obssp[j, ]) 
            if (is.na(de)){
              obssp$salinity_depth <- NA
            } else (de >= 1) {
              obssp$salinity_depth[j] <- extract(x=temp_brick[[de]], y = obssp[j, ])
            }
           }

```{r}
obssp$salinity_depth
```

>>>>

```{r}
netcdf_list <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf){  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working one
  brkyr <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 1)) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 2)) # extracting the second part of the netcdf filename (which is the month)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:nrow(obssp)) {  
      print (j)
      de <- obssp$depth[[j]]  # a variable for the observation depth layer
      yr <- (obssp$year[j])  # a variable for the observation year
      mth <- (obssp$month[j])  # a variable for the observation month
          if (brkyr == yr & brkmth == mth){
            obssp$salinity_surface[j] <- extract(x=temp_brick[[1]], y = obssp[j, ]) 
            if (is.na(de)){
              obssp$salinity_depth[j] <- NA
            } else  
              obssp$salinity_depth[j] <- extract(x=temp_brick[[de]], y = obssp[j, ])
          }
    }
}
```

```{r}
obssp$salinity_surface
```
above works!

Just play to see if you can get the variable thingy in....

```{r}
netcdf_list <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/testnetcdf/salinity", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf){  
  print(netcdf_name[i]) #this just prints the name of the netCDF R is working one
  brkyr <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 1)) # extracting the first part of the netcdf filename (which is the year)
  brkmth <- as.integer(sapply(strsplit(netcdf_name[i], "_"), "[[", 2)) # extracting the second part of the netcdf filename (which is the month)
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) 
    for (j in 1:nrow(obssp)) {  
      print (j)
      de <- obssp$depth[[j]]  # a variable for the observation depth layer
      yr <- (obssp$year[j])  # a variable for the observation year
      mth <- (obssp$month[j])  # a variable for the observation month
          if (brkyr == yr & brkmth == mth){
            obssp$salinity_surface[j] <- extract(x=temp_brick[[1]], y = obssp[j, ]) 
            if (is.na(de)){
              obssp$salinity_depth[j] <- NA
            } else  
              obssp$salinity_depth[j] <- extract(x=temp_brick[[de]], y = obssp[j, ])
          }
    }
}
```
